\section{Introduction and Motivation}
\label{sec:intro}

The Scottish COVID-19 Response Consortium (SCRC) \cite{2020University}, in collaboration with the Royal Society's call to action in March 2020, has taken a proactive approach to address the need for enhanced epidemiological models of COVID-19 transmission.
This joint effort, known as Rapid Assistance in Modelling the Pandemic (RAMP) \cite{2020Rapid}, aims to foster a deeper comprehension of the consequences associated with various exit strategies from lockdown measures.
Moreover, this consortium has attracted the involvement of distinguished scientists and experts from diverse organizations both within the United Kingdom and abroad, thus augmenting the collective knowledge base and ensuring comprehensive expertise in specialized domains.

RAMPVis \cite{2020Visualization} is a group of volunteers specialized in Data Visualization and Visual Analytics (abbreviated as VIS).
This group has willingly come forward to lend its specialized skills and knowledge in order to provide invaluable support to the consortium's modelers and epidemiologists.

Serving as the volunteer team responsible for providing visualization support to one of the six epidemiological models developed by the SCRC modelers \cite{chen2022RAMPVIS}, our main objective is to provide VIS researchers and practitioners with valuable insights gleaned from our research and development (R\&D) activities conducted during the COVID-19 pandemic.
In an effort to predict the potential impact of diverse interventions, both modelers and epidemiologists have actively utilized COVID-19 data, employing a method known as Uncertainty Quantification (UQ).
This process seeks to measure uncertainties through the application of mathematical models and simulations.
However, the modelers are confronted with significant challenges, including the aspects of expert elicitation and effective communication.
In other words, there is a need for software engineering effort coupled with visualization to provide support for the validation and verification tests, and to create efficient workflows between the modelers and the epidemiologists \cite{ackland2022Royal}.

In addressing these hurdles, \ac{VIS} emerges as a potent tool, offering the capacity to significantly enhance and streamline their collaborative workflows \cite{swallow2022Challenges}.
While our work may not have showcased the state-of-the-art VIS techniques, it effectively delivered rapid and practical VIS support to the modelers during an exceptional and demanding time.
The exemplification of a fully-virtual collaboration among researchers from various UK institutions epitomizes the spirit of interdisciplinary cooperation in the fight against the pandemic.


